
---
title: "week2_homework"
author: "Hanyu Zhao"
date: "12/10/2021"

output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true    
    number_sections: true
---

# Useful Functions

Create a vector

```{r, eval=FALSE}
c()
```

Return the length of a vector

```{r, eval=FALSE}
length()
```

Check the names of a vector or add names to a vector

```{r, eval=FALSE}
names()
```

Sort a vector by value

```{r, eval=FALSE}
sort()
```

Make a vector into a factor

```{r, eval=FALSE}
as.factor()
```

Generate random numbers from a uniform distribution

```{r, eval=FALSE}
runif()
```

Add up the values of a vector

```{r, eval=FALSE}
sum()
```

Calculate the average of the values of a vector

```{r, eval=FALSE}
mean()
```

Round a vector to the nearest...

```{r, eval=FALSE}
round()
```

Square root of the values in a vector

```{r, eval=FALSE}
sqrt()
```

Create a function

```{r, eval=FALSE}
function()
```

Return the desire object from a function

```{r, eval=FALSE}
return()
```


# TBC...
## test1
define a function:
def....