---
title: "Week3_Homework"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1
*load to_sort_pop_1.csv and to_sort_pop_1.csv from bioinformatics_data on github.
```{r}
##load vroom
library(vroom)
##read in the data files
sort_pop_1 <- vroom("C:/Users/bw21167/Desktop/bioinformatics/Data/to_sort_pop_1.csv")
sort_pop_2 <- vroom("C:/Users/bw21167/Desktop/bioinformatics/Data/to_sort_pop_2.csv")
```
## Task 2
*these two data are shown as below:
```{r}
sort_pop_1
sort_pop_2
```
The first four columns should be self explanatory (the species binomial, and the primary, secondary, and tertiary threat each species is being threatened by). The rest of the columns specify the population counts for given dates.

## Task 3
*using tidyverse join both of these data together into a single tibble
```{r}
##load the tidyverse
library("tidyverse")
##use full_join to join these data into a single tibble as sort_pop
sort_pop <- full_join(sort_pop_1, sort_pop_2)
##look at sort_pop
sort_pop
```

## Task 4
*reshape them from wide to long format
```{r}
##our data frame
sort_pop_long <- sort_pop %>%
  ##and then apply this function to shape data from wide to long format
  ##keep the four columns: species; primary_threat; secondary_threat; tertiary_threat
  ##and add population, date and abundance
  pivot_longer(cols = -c(species:tertiary_threat),
               names_to = c("population", "date"),
               names_pattern = "(.*)_(.*)",
               values_drop_na = F,
               values_to = "abundance")
##look at the long format data
sort_pop_long
```